Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2015-06-02 tese/project.tex
Reviewed the conclusions

\section{Conclusions}\label{concl} % English
  The development of WebRTC by the World Wide Web Consortium (W3C) allows web browser-to-browser audio, video and data communication. WebRTC is enabling new usage scenarios for communication and collaboration applications. However, the nature of such scenarios lead to significant challenges, such as the need to record interactive audio and video streams.

@@

>>>>

\section{Conclusions}\label{concl} % English
The development of WebRTC by the World Wide Web Consortium (W3C) allows web browser-to-browser audio, video and data communication. WebRTC is enabling new usage scenarios for communication and collaboration applications. This and other technologies allow the Hyper-link concept to be applied to a new media: real-time audio and video.

@@

  A prototype will be implemented in order to validate these concepts.
In order to implement it, significant challenges, such as the need to record interactive audio and video streams, will have to be overcome, making this a challenging project.
